European or American? A re-examination of the transatlantic influence over the IMF

### 2025-05-22 manuscript/manuscript.qmd
Add covariates

>>>>

## Covariates

The existing literature has identified several factors beyond geopolitical alignment that influence IMF lending decisions or a country's demand for IMF assistance. We include these variables as covariates to account for potential confounding effects. Notably, countries with larger IMF quotas (and thus greater voting power), as well as those with nationals among IMF staff, are expected to receive more favourable treatment from the Fund [@barro2005].

We also include economic performance indicators such as GDP, per capita GDP, and lagged GDP growth as determinants of lending and borrowing behaviour. International reserves as a share of imports are used to capture a country’s ability to finance its balance of payments without IMF support. Finally, a binary indicator for OECD membership is included to proxy for institutional and economic differences among countries.

The selection of covariates, including their polynomial transformations[^8], closely follows @lipscy2018 and @barro2005 to ensure comparability with previous findings.

[^8]: Quadratic terms are included for GDP and per capita GDP to capture potential non-linear effects. See [Model Specification] for details.

## Model Specification {#sec-model}
